### 2010-12-28 Documentation/atropos/atropos.tex
ENH:  A few minor edits.
git-svn-id: https://advants.svn.sourceforge.net/svnroot/advants@727 fd2da0a4-d968-48df-9cb5-d8c496287cbf

\caption{\baselineskip 12pt \small Brainweb single-subject results for

@@

\caption{\baselineskip 12pt \small Brainweb 20-subject results for

@@

We first convert each of the 69 labels within the original evaluation
dataset to an individual image.  The remaining steps,
summarized briefly, are the same for each of the 19 subjects.  We
select one subject as an unlabeled target.  The other 18 datasets are
then mapped (as in the script above) to that subject.  We then deform,
individually, the 69 $\times$ 18 label images to the unlabeled
subject.  The label probability map is gained by averaging the 18
deformed images associated with each label.  We repeat this for each
subject.  The following parameters are the most relevant to this discussion:
{\ttfamily  -i  PriorProbabilityImages[3, label\_prob\%02d.nii.gz,0.5] 
-m [0.1,1x1x1] -c [5,0] -p Socrates[1] }.  Results, in terms of
Dice overlap, are shown in figure~\ref{fig:hammers}.
\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[height=8in]{Figures/final_results_majority_vote_vs_atropos.pdf}
\end{tabular}
\caption{\baselineskip 12pt \small The figure compares the Dice
overlap results from Atropos versus the raw results from majority
voting for each of 68 neuroanatomical regions and, in addition, the
unlabeled portions of the brain from the Hammers evaluation dataset.
We evaluated Atropos via N-fold cross-validation and employed
PriorProbabilityImages for each class where probabilities are gained
by averaging mapped subject labels. The color coding highlights those
regions that have the highest (yellow) and lowest (pink) improvement.
The significance of the improvement, measured by pairwise T-test, is
also shown as is a trinary coding of that improvement as: $+$
significant improvement, $-$ performance reduction, $\sim$ no change.}
\label{fig:hammers}
\end{center}
\end{figure}

@@

\subsection{Performance on Brainweb Data}
Atropos results are competitive with the state of the art.  For
instance, \cite{Ashburner2005} (SPM5) evaluated on 0\% RF (bias field) 3\%
noise brainweb single subject data finding 0.932 (GM) and .961 (WM)
Dice. Results on 40\% RF were .934 (GM) and .961 (WM). SPM5 exhibits
insensitivity to bias similar to our own best results on the 40\%RF, 3
\% noise case (MRF-$\beta$=0.2, Kmeans $+$ N4) with Dice for GM is
0.950737 and for WM is 0.962586.  \cite{Nakamura2009} gave GM Dice
results (brainweb single 3\% noise) of 0.962 (0\%RF), 0.964(20\%RF)
and .956(40\%RF) which are slightly higher than either SPM5 or Atropos
results.  However, \cite{Nakamura2009} do not report WM or CSF numbers
for comparison.  Topology preserving methods also perform well.
\cite{Shiee2010} achieved Dice results for 3\% noise 20\% RF brainweb
single subject with 0.927, 0.912 and 0.900 for WM, GM and CSF,
respectively.  These are excellent numbers given the additional
constraint applied to the segmentation.  
\cite{Bazin2007c} proposed TOADS and, estimating from the
paper's graph, showed that the average Dice accuracy for 3\% noise various RF was
.95-.96 for WM, .93-.95 for GM and .92-.94 for CSF.
Perhaps the most recent balanced evaluation was performed in
\citep{Klauschen2009}, which reports confusion matrix numbers, rather
than Dice overlap.  Because the absolute true number of GM and WM
voxels for brainweb are known, we can convert the confusion matrix to
Dice.  In that case, the SPM5 Dice for brainweb single GM and WM is .8847
and .9085, respectively, while FreeSurfer and FSL's accuracy is
lower. The best GM result for 20 subjects is obtained by SPM5: 0.9295;
best WM Dice is from FSL: 0.9499.  We note that \cite{Klauschen2009}
used a comprehensive evaluation where quality of brain extraction also
contributed to the outcome.  Thus, the results must be interpreted
slightly differently than those from other papers.

>>>>

\caption{\baselineskip 12pt \small BrainWeb single-subject results for

@@

\caption{\baselineskip 12pt \small BrainWeb 20-subject results for

@@

We first convert each of the 69 labels within the original evaluation
dataset to an individual image.  The remaining steps,
summarized briefly, are the same for each of the 19 subjects.  We
select one subject as an unlabeled target.  The other 18 datasets are
then mapped (as in the script above) to that subject.  We then deform,
individually, the 69 $\times$ 18 label images to the unlabeled
subject.  The label probability map is gained by averaging the 18
deformed images associated with each label.  We repeat this for each
subject.  The following parameters are the most relevant to this discussion:
{\ttfamily  -i  PriorProbabilityImages[3,label\_prob\%02d.nii.gz,0.5] 
-m [0.1,1x1x1] -c [5,0] -p Socrates[1] }.  Results, in terms of
Dice overlap, are shown in figure~\ref{fig:hammers}.
\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[height=8in]{Figures/final_results_majority_vote_vs_atropos.pdf}
\end{tabular}
\caption{\baselineskip 12pt \small The figure compares the Dice
overlap results from Atropos versus the raw results from majority
voting for each of 68 neuroanatomical regions and, in addition, the
unlabeled portions of the brain from the Hammers evaluation dataset.
We evaluated Atropos via N-fold cross-validation and employed
PriorProbabilityImages for each class where probabilities are gained
by averaging mapped subject labels. The color coding highlights those
regions that have the highest (yellow) and lowest (pink) improvement.
The significance of the improvement, measured by pairwise T-test, is
also shown as is a trinary coding of that improvement as: $+$
significant improvement, $-$ performance reduction, $\sim$ no change.}
\label{fig:hammers}
\end{center}
\end{figure}

@@

\subsection{Performance on BrainWeb Data}
Atropos results are competitive with the state of the art.  For
instance, \cite{Ashburner2005} (SPM5) evaluated on 0\% RF (bias field) 3\%
noise brainweb single subject data finding 0.932 (GM) and .961 (WM)
Dice. Results on 40\% RF were 0.934 (GM) and 0.961 (WM). SPM5 exhibits
insensitivity to bias similar to our own best results on the 40\%RF, 3\% 
noise case (MRF-$\beta$=0.2, K-means $+$ N4) with Dice for GM is
0.950737 and for WM is 0.962586.  \cite{Nakamura2009} gave GM Dice
results (brainweb single 3\% noise) of 0.962 (0\%RF), 0.964(20\%RF)
and 0.956(40\%RF) which are slightly higher than either SPM5 or Atropos
results.  However, \cite{Nakamura2009} do not report WM or CSF numbers
for comparison.  Topology preserving methods also perform well.
\cite{Shiee2010} achieved Dice results for 3\% noise 20\% RF brainweb
single subject with 0.927, 0.912 and 0.900 for WM, GM and CSF,
respectively.  These are excellent numbers given the additional
constraint applied to the segmentation.  
\cite{Bazin2007c} proposed TOADS and, estimating from the
paper's graph, showed that the average Dice accuracy for 3\% noise various RF was
0.95-0.96 for WM, 0.93-0.95 for GM and 0.92-0.94 for CSF.
Perhaps the most recent balanced evaluation was performed in
\citep{Klauschen2009}, which reports confusion matrix numbers, rather
than Dice overlap.  Because the absolute true number of GM and WM
voxels for brainweb are known, we can convert the confusion matrix to
Dice.  In that case, the SPM5 Dice for brainweb single GM and WM is 0.8847
and 0.9085, respectively, while FreeSurfer and FSL's accuracy is
lower. The best GM result for 20 subjects is obtained by SPM5: 0.9295;
best WM Dice is from FSL: 0.9499.  We note that \cite{Klauschen2009}
used a comprehensive evaluation where quality of brain extraction also
contributed to the outcome.  Thus, the results must be interpreted
slightly differently than those from other papers.
